---
title: "p8105_hw1_hq2163"
author: "Hanbo Qiu"
date: "September 18, 2018"
output: github_document
---

Problem 1  
------------------------------------------------------------

###This problem focuses on variable types and coercion.

### Create a data frame for Problem 1:

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r creat_dataframe}
set.seed(2163)

dataframe_problem1 = tibble(
  vec_numeric = rnorm(10, sd = 5),
  vec_logical = vec_numeric > 2,
  vec_char = c("Please", "list", "the", "American", "people's", "top", "four", "most", "popular", "sports"),
  vec_factor = factor(c("football", "basketball", "baseball", "ice_hockey", "football", "basketball", "baseball", "ice_hockey", "football", "basketball"))
)
```
### Try to take the mean of each variable in my dataframe:

```{r vec_mean}
mean(dataframe_problem1$vec_numeric)
mean(dataframe_problem1$vec_logical)
mean(dataframe_problem1$vec_char)
mean(dataframe_problem1$vec_factor)
```

* It shows that the mean of vec_numeric is `r mean(dataframe_problem1$vec_numeric)`
* It shows that the mean of vec_logical is `r mean(dataframe_problem1$vec_logical)`
* It shows that mean function can work well for numeric and logical vectors but doesn't work for    characteristic vectors and vectors as factors.
