---
title: "p8105_hw1_hq2163"
author: "Hanbo Qiu"
date: "September 18, 2018"
output: github_document
---

Problem 1  
------------------------------------------------------------

###This problem focuses on variable types and coercion.

### Create a data frame for Problem 1:

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r creat_dataframe}
set.seed(2163)

dataframe_problem1 = tibble(
  vec_numeric = rnorm(10, sd = 5),
  vec_logical = vec_numeric > 2,
  vec_char = c("Please", "list", "the", "American", "people's", "top", "four", "most", "popular", "sports"),
  vec_factor = factor(c("football", "basketball", "baseball", "ice_hockey", "football", "basketball", "baseball", "ice_hockey", "football", "basketball"))
)
```
### Try to take the mean of each variable in my dataframe:

```{r vec_mean}
mean(dataframe_problem1$vec_numeric)
mean(dataframe_problem1$vec_logical)
mean(dataframe_problem1$vec_char)
mean(dataframe_problem1$vec_factor)
```

* It shows that the mean of vec_numeric is `r mean(dataframe_problem1$vec_numeric)`
* It shows that the mean of vec_logical is `r mean(dataframe_problem1$vec_logical)`
* It shows that mean function can work well for numeric and logical vectors but doesn't work for    characteristic vectors and vectors as factors.

### convert variables from one type to another:

```{r eval = FALSE}
as.numeric(dataframe_problem1$vec_logical)
as.numeric(dataframe_problem1$vec_char)
as.numeric(dataframe_problem1$vec_factor)
```

###convert my character variable from character to factor to numeric
###convert my factor variable from factor to character to numeric

```{r convert_variables}
newvec_factor = as.factor(dataframe_problem1$vec_char)
as.numeric(newvec_factor)
newvec_char = as.character(dataframe_problem1$vec_factor)
as.numeric(newvec_char)
```

Problem 2  
------------------------------------------------------------

###This problem focuses on plotting and the use of inline R code.

### Create a data frame for Problem 2:

```{r, include = FALSE}
library(tidyverse)
```

```{r plot_df}
plot_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec_logical2 = (x + y) > 0,
  vec_numeric2 = as.numeric(vec_logical2),
  vec_factor2 = as.factor(vec_logical2)
)
```

### A short description of my vector:

* the size of the dataset is `r nrow(plot_df)`*`r ncol(plot_df)`.
* the mean of x is `r mean(plot_df$x)`
* the median of x is `r median(plot_df$x)`
* the proportion of cases for which the logical vector is TRUE is `r sum(plot_df$vec_logical2)/1000`

### Make a scatterplot of y vs x:

```{r}
ggplot(plot_df, aes(x , y, color=vec_logical2))+ geom_point()
```

###The first picture is a scatterplot of y vs vec_logical2. The red spots represent x+y<0(vec_logical2=FALSE) and the green spots represent x+y>0(vec_logical2=TRUE.)

```{r}
ggsave("logical_plot.tiff")
```

```{r}
ggplot(plot_df, aes(x , y, color=vec_numeric2))+ geom_point()
```

###The second picture is a scatterplot of y vs vec_numeric2. The dark blue spots represent vec_numeric2=0 and the light blue spots represent vec_numeric2=1.

```{r}
ggplot(plot_df, aes(x , y, color=vec_factor2))+ geom_point()
```

###The third picture is a scatterplot of y vs vec_factor2. The red spots represent vec_factor2=FALSE and the green spots represent vec_factor2=TRUE.
